---
title: "Paolo Mean Fourier Profile"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data loading

The sub40 folder contains only high-quality time series: they are complete (i.e. going from time 0 to 243 without break) and potential missing values were imputed via linear interpolation. Each file corresponds to a different cell treatment.

Start with WT cells, stimulated with EGF 1 ng/mL.

```{r}
library(data.table)
library(ggplot2)
library(plyr)
library(stringr)
dt <- fread("/home/marc/Dropbox/Work/image_analysis/data/paolo/sub40/condition2.csv")
head(dt)

# Default ggplot theme
theme_set(theme_bw())

col_fluo <- colnames(dt)[c(7,8,11:14)]
dt_melt <- melt(dt, measure.vars = col_fluo)
ggplot(dt_melt, aes(x=Image_Metadata_T, y=value)) +
  geom_line(aes(group=uniqID)) +
  facet_wrap(~variable, ncol = 2, scales = "free") +
  stat_summary(fun.y = "mean", geom = "line", col = "blue", size = 1.3)
```

## Mean Power Profile

```{r}
dt_freq <- dt[, .(freq = spectrum(objNuclei_Intensity_MeanIntensity_imKTR, plot=FALSE)$freq,
                  spec = spectrum(objNuclei_Intensity_MeanIntensity_imKTR, plot=FALSE)$spec),
                  by = uniqID]

dt_freqProfile <- dt_freq[, .(spec = mean(spec)), by = freq]
```

```{r}
ggplot(dt_freqProfile, aes(x=freq, y=spec)) +
  geom_col() +
  scale_y_continuous(labels = scales::scientific)
```

## Trajectoy associated with frequency profile

data.table cannot handle complex numbers so go to for loop

```{r}
v.ID <- unique(dt$uniqID)
# Matrix which contain the Fourier transform for each trajectory
init.mat <- matrix(0+0i, ncol = length(unique(dt$Image_Metadata_T)), nrow = length(v.ID))
for(i in 1:length(v.ID)){
  ID <- v.ID[i]
  init.mat[i,] <- fft(dt[uniqID==ID, objNuclei_Intensity_MeanIntensity_imKTR])
}
mean.profile <- colMeans(init.mat)
mean.traj <- Re(fft(mean.profile, inverse = T))
plot(mean.traj, type="l")
```


## Repeat for all condtions and compare mean Power profiles

### Load all data

```{r}
# Clean workspace
rm(dt, dt_freq, dt_freqProfile, dt_melt)

# Efficiently read all CSVs and combine in a single data.table
path <- "/home/marc/Dropbox/Work/image_analysis/data/paolo/sub40/"
files <- paste0(path, list.files(path))
dt <- as.data.table(rbind.fill(lapply(files, fread, header=TRUE)))
rm(files, path)
```

Make a table of correspondance well <--> human readable treatment.

```{r}
dt_treatment <- dt[, .(Image_Metadata_Well, condAll)]
setkey(dt_treatment, "Image_Metadata_Well")
dt_treatment <- unique(dt_treatment)
dt_treatment[, Mutation := str_extract(condAll, "_[A-Z0-9\\-/]+?_")][, Mutation := substr(Mutation, 2, nchar(Mutation)-1)]
dt_treatment[, EGF := str_detect(condAll, "EGF_1")]
dt_treatment$EGF <- ifelse(dt_treatment$EGF, "+EGF", "")
dt_treatment[, Condition := paste0(Mutation, EGF)]
setnames(dt_treatment, "Image_Metadata_Well", "Well")
dt_treatment <- dt_treatment[, .(Well, Condition)]
```

### Power profile

```{r}
dt_freq <- dt[, .(freq = spectrum(objNuclei_Intensity_MeanIntensity_imKTR, plot=FALSE)$freq,
                  spec = spectrum(objNuclei_Intensity_MeanIntensity_imKTR, plot=FALSE)$spec),
                  by = uniqID]
dt_freq[, Well := str_sub(uniqID, 1 , 2)]
dt_freqProfile <- dt_freq[, .(mean.spec = mean(spec), median.spec = median(spec)), by = .(Well,freq)]
# Human readable condition
dt_freqProfile <- merge(dt_freqProfile, dt_treatment, by = "Well")
```

#### Mean profile

```{r fig.height=12}
ggplot(dt_freqProfile, aes(x=freq, y=mean.spec)) +
  geom_col() +
  facet_wrap(~Condition, scales = "free", ncol = 2) +
  scale_y_continuous(labels = scales::scientific) + 
  scale_x_continuous(limits = c(0,0.2)) +
  theme(text = element_text(size=20))
```


#### Median profile

```{r fig.height=12}
ggplot(dt_freqProfile, aes(x=freq, y=median.spec)) +
  geom_col() +
  facet_wrap(~Condition, scales = "free", ncol = 2) +
  scale_y_continuous(labels = scales::scientific) + 
  scale_x_continuous(limits = c(0,0.2)) +
    theme(text = element_text(size=20))
```

Frequencies of the peak:

```{r}
dt_topfreq <- dt_freqProfile[, .(median.spec = tail(sort(median.spec),3)), by=Condition]
dt_topfreq <- merge(dt_topfreq, dt_freqProfile, by="median.spec", all.y = F)
dt_topfreq[, c("Condition.y", "Well") := list(NULL, NULL)]
setkey(dt_topfreq, "Condition.x", "median.spec")
setcolorder(dt_topfreq, c("Condition.x", "freq", "median.spec", "mean.spec"))
# TO CHECK: if fqctor 2 the right thing to do to switch to period?
dt_topfreq[, period := 1/(2*freq)]
dt_topfreq
```



#### Mean trajectoy in time space

```{r fig.height=12}
dt_melt <- melt(dt, measure.vars = "objNuclei_Intensity_MeanIntensity_imKTR")
dt_melt[, Well := str_sub(uniqID, 1, 2)]
dt_melt <- merge(dt_melt, dt_treatment, by = "Well")

ggplot(dt_melt, aes(x=Image_Metadata_T, y=value)) +
  geom_line(aes(group=uniqID)) + 
  facet_wrap(~Condition, ncol=2, scales = "free") +
  stat_summary(fun.y="mean", geom="line", col="blue", size=2)
```

Can't see much.

#### Get mean profile in frequency space and reconstruct corresponding trajectory in time space

data.table cannot handle complex numbers so go to for loop.

```{r fig.height=12}
setkey(dt, uniqID)
v.ID <- unique(dt$uniqID)
# Matrix which contain the Fourier transform for each trajectory
init.mat <- matrix(0+0i, ncol = length(unique(dt$Image_Metadata_T)), nrow = length(v.ID))
for(i in 1:length(v.ID)){
  ID <- v.ID[i]
  init.mat[i,] <- fft(dt[uniqID==ID, objNuclei_Intensity_MeanIntensity_imKTR])
}

# Each group of 40 rows is related to a condition
par(mfrow=c(7,2))
for(i in seq(1, nrow(init.mat), by = 40)){
  mean.profile <- colMeans(init.mat[i:(i+39),])
  mean.traj <- Re(fft(mean.profile, inverse = T))
  mean.traj <- mean.traj / length(mean.traj)
  plot(mean.traj, type="l", main = dt_treatment[Well==str_sub(v.ID[i], 1, 2), Condition])
}

```

Looks like this recover the mean trajectories that are found in time space. Levels are shifted.
